Matrix Transposition and Symmetry: a case study on Superscalar Architectures\\

### 2024-11-25 latex/paper.tex
latex: state of the art draft

Computing the transpose of a matrix is a well discussed problem.

Older fortran implementations were difficult due to fortran.

>>>>

Computing the transpose of a matrix is a well discussed problem. Earlier
work focus on in-situ transporision, that is transposing a matrix without
relying on additional space. The implementations often exploit the acyclic
structure of the transposition mapping since values of a matrix of size $N$ can be stored
in a single contiguous array or size $N$*$N$ and indexed with $row*#rows+ column$.
Remarcable contributions include Boothroyd's ACM Algorithm 302
presented in 1966\cite{b?}, the 1970 revision by Laflin and Brefner
in ACS Algorithm 380 and a later revision with ACM Algorithm 513 /* TODO SOURCES and names */.

SIMD implementations have also been studied

Another class of algorithms include out-of-core matrix transposition, that
is computing the transpose of a matrix that is too big to fit in memory.
This problem focuses on minimizing the number of I/O operations since memory-memory data transfer
is notably slower than math operations. Work in out-of-core transposition include /*TODO*/

GPU /* TODO */
